\begin{thebibliography}{100}

\subsection*{Books}

	\bibitem{alain} Abran A., {\em Software Metrics and Software Metrology}, IEEE Computer Society, Los Alamitos, 2010.	
	
	\bibitem{graph} Berge C., {\em Theory of Graphs}, Dover Publications, 2001. 
	
	\bibitem{booch} Booch G., {\em Object-Oriented Analysis and Design with Applications}, Addison-Wesley, 2007.
	
	\bibitem{rigorous} Fenton N., Pfleeger S., {\em Software Metrics - A Rigorous And Practical Approach}, PWS Publishing Company, Boston, 1997.
	
	\bibitem{metrics} Kan S., {\em Metrics and Models in Software Quality Engineering}, Addison Wesley, 2002.

	\bibitem{moodbook} Sarker M., {\em An overview of Object Oriented Design Metrics}, Department of Computer Science at Sweden Umea University, Umea, 2005.
		
	\bibitem{SCJP} Sierra K., Bates B., {\em Sun Certified Programmer for Java 6}, Mc Graw Hill, 2008.
	
\subsection*{Online documents}

	\bibitem{complexity1} Aivosto.com, {\em Complexity metrics}, [access: November 9, 2013]. \\ Available at: \url{http://www.aivosto.com/project/help/pm-complexity.html}. 
	
	\bibitem{directedGraph} Algorithms Overview, {\em A directed graphs}, [access: November 9, 2013].\\  Available at: \url{http://algs4.cs.princeton.edu/42directed/}.

\bibitem{indie} Chawla M. K., Chhabra I., {\em }, Department of Computer Science Department in Panjab University in Chandigarh (India), [access: November 17,2013]. Available at: \url{http://tnijurl.com/f97365e79185/}.

	\bibitem{coverage1} Cornett S., {\em Code Coverage Analysis}, [access: November 3, 2013]. Available at: \url{http://www.bullseye.com/coverage.html}.

	\bibitem{ISO9126} ISO 9126 Software Quality Characteristics,{\em An overview of the ISO 9126-1 software quality model definition, with an explanation of the major characteristics}, [access: November 26, 2013]. Available at: \url{http://www.sqa.net/iso9126.html}.

	\bibitem{JavaDoc} Java Tutorials, The, {\em Polymorphism}, [access: October 7, 2013]. Available at: \\ \url{http://docs.oracle.com/javase/tutorial/java/IandI/polymorphism.html}.	
	
	\bibitem{coverage2} Johnson P., {\em Testing and Code Coverage}, [access: November 3, 2013]. Available at: \url{http://pjcj.net/testing_and_code_coverage/paper.html}.

	\bibitem{vaxjo} Lincke R, Lundberg J., Lowe W., {\em Comparing Software Metrics Tools}, School of Mathematics and Systems Engineering in Vaxjo University in Sweden, [access: November 17, 2013]. Available at: \url{http://www.cs.umd.edu/~pugh/ISSTA08/issta2008/p131.pdf}.
 
	\bibitem{cccc1} Littlefair T., {\em CCCC. User Guide}, [access: November 17, 2013]. Available at: \url{http://www.stderr.org/doc/cccc/CCCC\%20User\%20Guide.html}. 

	\bibitem{stan} Odysseus Software GmbH, {\em STAN – Structure Analysis for Java}, [access: November 16, 2013]. Available at: \url{http://stan4j.com/papers/stan-whitepaper.pdf}. 
 	
	\bibitem{martin} Martin R. {\em OO Design Quality Metrics. An Analysis of Dependencies}, [access: November 11, 2013]. Available at: \url{http://www.cin.ufpe.br/~alt/mestrado/oodmetrc.pdf}.
	
	\bibitem{nasa} Rosenberg L., {\em Applying and Interpreting Object Oriented Metrics}, Software Assurance Technology Center (SATC) in NASA, [access: November 9, 2013]. Available at: \url{http://www.literateprogramming.com/ooapply.pdf}.
 
\end{thebibliography}